Observing Earth as an Exoplanet with \TESS: Photometric Mapping of Surface Features in Reflected Light

### 2019-05-02 tex/ms.tex
working on intro

However, obtaining a map of a temperate terrestrial exoplanet is still
beyond the capabilities of current facilities, as both the thermal and 
reflected light signals from these planets
are orders of magnitude below current measurement capabilities. Nevertheless,
much work has been done on the theoretical front on mapping terrestrial
planets in the habitable zone
\citep[e.g.,][]{Kawahara2010,Fujii2012,Berdyugina2017,Haggard2018,Lustig-Yaeger2018};
for a review, see \cite{Cowan2018}.

\todo{(THIS PARAGRAPH TO BE CHANGED:)} 
In this work, we show how we can harness photometric data collected by the \TESS mission
to construct a map of Earth, a rocky planet with a radius of $6.4\times 10^6$~m
orbiting near the inner edge of the habitable zone of its star, a nearby G2 main sequence
star \citep{Sagan1993}. Although the \TESS mission promised to deliver a handful of terrestrial planets in 
the habitable zone for follow-up with other missions, it came as a great surprise
that data from the spacecraft could be used not only to detect Earth but to
characterize it in detail. This is due primarily to the strong nature of the reflected
light signal originating from the planet, which 
because of complex internal optics illuminates the entirety of the \TESS detector 
during most of Sector 1 and part of Sector 2.

Previous attempts to map Earth from the exoplanet community have suggested 
the presence of localized surface features, but their resolving power has been 
limited by the cadence and/or duration of observations \citep{Cowan2009,Jiang2018}. 
\TESS offers precise 2-minute cadence data spanning a wide range of illumination 
phases, enabling a level of spatial and temporal resolving power that is 
unprecedented in the history of exoplanet phase mapping. 
%
Moreover, recent advances on the modeling side 
have made the reconstruction of detailed maps more feasible than ever. 
\cite{Luger2019} developed an analytic algorithm for generating---and
inverting---light curves of stars and planets whose surface emission is
described in terms of spherical harmonics, dubbed \starry. The analyticity of this
method makes the computation of the model both fast and precise.
In turn, \cite{Haggard2018} derived analytic expressions for the
analogous case in reflected light, packaged into the 
\textsf{EARL} code. In this work, we derive similar expressions within
the \starry framework to perform fast, analytical inversion of the light curve
of Earth and thus construct a map of the planet in reflected light.

>>>>

However, obtaining a map of a temperate terrestrial exoplanet is still
beyond the capabilities of current facilities, as both the thermal and 
reflected light signals from these planets
are orders of magnitude below current measurement capabilities. Nevertheless,
much work has been done on the theoretical front on mapping terrestrial
planets in the habitable zone
\citep[e.g.,][]{Ford2001,Tinetti2006a,Tinetti2006b,WilliamsGaidos2008,Palle2008,
Kawahara2010,Fujii2012,Berdyugina2017,Haggard2018,Lustig-Yaeger2018};
for a review, see \cite{Cowan2018}. In particular, several works
have harnessed space-based observations of the Earth in proof-of-concept
studies aimed at shedding light on the opportunities and challenges future
exoplanet mapping missions may bring. Perhaps the most well-known of these
is the work of \cite{Sagan1993}, who used observations from the Galileo probe
to infer the existence of life on Earth. However, this study made use of both
spectroscopic observations and spatially-resolved images of the planet at high
resolution. \cite{Goode2001} and \cite{Woolf2002} used unresolved measurements of
Earthshine reflecting off the face of the Moon to infer the planet's
seasonally-variable albedo and its atmospheric transmission spectrum,
respectively. \cite{Cowan2009} used unresolved images of the Earth taken
by the EPOXI spacecraft to construct low resolution albedo maps, recovering
approximate longitudinal distributions of oceans continents on the planet. More
recently, \cite{Jiang2018} made use of daily images of the fully-illuminated
disk of the Earth taken by the Deep Space Climate Observatory (DSCOVR) to recover
the planet's rotation rate and seasonal albedo variations.

In all of these studies, ...

resolving power has been 
limited by the cadence and/or duration of observations
\TESS offers precise 2-minute cadence data spanning a wide range of illumination 
phases, enabling a level of spatial and temporal resolving power that is 
unprecedented in the history of exoplanet phase mapping.

\citep{Sagan1993}.

%
Moreover, recent advances on the modeling side 
have made the reconstruction of detailed maps more feasible than ever. 
\cite{Luger2019} developed an analytic algorithm for generating---and
inverting---light curves of stars and planets whose surface emission is
described in terms of spherical harmonics, dubbed \starry. The analyticity of this
method makes the computation of the model both fast and precise.
In turn, \cite{Haggard2018} derived analytic expressions for the
analogous case in reflected light, packaged into the 
\textsf{EARL} code. In this work, we derive similar expressions within
the \starry framework to perform fast, analytical inversion of the light curve
of Earth and thus construct a map of the planet in reflected light.
